Real-Time Systems

### 2013-09-27 beamer/dit-paper-presentation.tex

\title {Real-Time Systems}
\subtitle {The Space of Feasible Execution Times for Asynchronous Periodic Task
Systems using Definitive Idle Times}
\author{Thomas Chapeaux \inst{1} \and Paul Rodriguez \inst{1} \and Laurent George \inst{2} \and Joël Goossens \inst{1}}
\institute[shortinst]{\inst{1} Université Libre de Bruxelles \and %
                      \inst{2} ECE Paris}
\date{July 2013}

@@

	\begin{frame}{Model}
		Tasks, jobs, OCDT
	\end{frame}

@@

	\begin{frame}{Related Works}
	This one and this one
	\end{frame}

@@

	\begin{frame}{Definition of the FPDIT}
		Even without knowing the WCETs in advance, we can define the following notions:
		\begin{block}{Definition}
			A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
			released strictly before instant $t$ has its absolute deadline before or at instant $t$.
		\end{block}
		\begin{block}{Definition}
			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{block}

@@

\section{C-space}

		A region of $\mathbb{N}_0^n$ such as the C-space can be described by a list of parametric linear constraints (called the \emph{formulation}).
	\end{frame}

	\subsection{Redundancies}

		\subsubsection{General approach}

		\begin{frame}{Redundancies}
			Infinite number of constraints...

			However: arrival and deadlines, feasibility interval, ILP

			The sequel will concentrate on obtaining a short feasibility interval
		\end{frame}

		\subsubsection{Synchronous systems}

		\begin{frame}{Redundancy in synchronous systems}
			[0, t] is a critical instant, 0 is the worst-case
		\end{frame}

		\subsubsection{Asynchronous systems}

>>>>

\title {Real-Time Systems}
\subtitle {The Space of Feasible Execution Times for Asynchronous Periodic Task
Systems using Definitive Idle Times}
\author{Thomas~Chapeaux~\inst{1}~\inst{2} \and Paul~Rodriguez~\inst{1}~\inst{2} \and Laurent~George~\inst{2} \and Joël~Goossens~\inst{1}}
\institute[shortinst]{\inst{1} Université Libre de Bruxelles \and %
                      \inst{2} ECE Paris}
\date{July 2013}

@@

	\begin{frame}{Model}
  \begin{block}{Definition}
  Systems with real-time constraints. (e.g. ABS, VOD, etc)
  \end{block}
  \textbf{Model:} Set of tasks $\tau_i = (O_i, T_i, D_i, C_i)$ generating jobs $J_{i,j}$, with
      \begin{itemize}
      \item $O_i$ : arrival of the first job
      \item $T_i$ : time between two jobs
      \item $D_i$ : relative deadline
      \item $C_i$ : execution time
    \end{itemize}

  \begin{columns}[c] % the "c" option specifies center vertical alignment
  \column{.4\textwidth}
\begin{center}
\begin{tabular}{|r|c|c|c|c|}
 \hline
  & $O_i$ & $T_i$ & $D_i$ & $C_i$ \\
 \hline
 $\tau_1$ & 1 & 2 & 6 & 10\\
 \hline
 $\tau_2$ & 0 & 3 & 5 & 5\\
 \hline
\end{tabular}
\end{center}

  \column{.6\textwidth} % column designated by a command
\begin{figure}[h]
\includegraphics[width=\textwidth]{figs/RTsystem_example.png}
\caption{A task system}
\label{fig:llf}
\end{figure}
  \end{columns}
\end{frame}

@@

    \subsubsection{The C-space}

        A region of $\mathbb{N}_0^n$ such as the C-space can be described by a list of parametric linear constraints (called the \emph{formulation}), such as those given by the DBF test.
    \end{frame}

    \begin{frame}{Removing Redundancies in the C-space of synchronous system}

@@

	\begin{frame}{Definition of the FPDIT}
		We define the following notions, which do not depend on the WCET values:
		\begin{block}{Definition}
			A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
			released strictly before instant $t$ has its absolute deadline before or at instant $t$.
		\end{block}
		\begin{block}{Definition}
			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{block}

@@

\section{C-space of asynchronous system}
